Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-04 manuscript.tex
5 updates

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{(top) The spurious RVs (black dots) caused by a facula in the simulated data using a Normal and a SN fit, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
   %
 (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr. std--red crosses) and the residuals from the usual correction (Usual corr. std--green triangles). The residuals have a smaller systematic component when using the proposed model of 
  Eq.~\ref{eq:RV:correction} (red crosses) compared to the usual model (green triangles).
The tests of statistical significance on the parameters are presented in Table \ref{table:faculae.test}.}
    \label{fig:faculae.correction}
\end{center}
\end{figure*}

@@

In the right of Fig.~\ref{fig:alphacent:corr.gamma}, we show the comparison between the RVs retrieved using the SN density and the ones obtained with the Normal density. We clearly see that the amplitude of the activity signal is stronger when using SN mean RV, and the signal measured using N mean RV or SN median RV are very similar. We observe the same behavior in the case of a faculae (see Sec.~\ref{sec:soap.faculae}) and therefore, it seems that the activity signal seen in those data os most likely induced by faculae. This is an observation that was already made in \citet{Dumusque-2014c}.
%When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting. This happens because the mean of the SN is more sensitive to stellar activity. In fact, because the SN includes an asymmetry parameter, SN mean RV gets more shifted in the direction of the asymmetry induced by stellar activity. On the other hand, when using SN median RV, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean. The bottom plot of Fig.~\ref{fig:alphacent:diff:RV} captures this aspect. Both indicators can be used to capture and summarise the different information available in the CCF, as will be shown in the remainder of this work.
%%
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[height = 3in]{HD12862_[2]RadialVelocityDifferences.pdf} 
%   \caption{(top) RVs as function of Julian Day for Alpha Centauri B. The RVs are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses). (bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan crosses).}
%   \label{fig:alphacent:diff:RV}
%\end{figure*}
%

>>>>

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{(top) The spurious RVs (black dots) caused by a facula in the simulated data using a Normal and a SN fit, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.  
  %
 (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr. std--red crosses) and the residuals from the usual correction (Usual corr. std--green triangles). The residuals have a smaller systematic component when using the proposed model of 
  Eq.~\ref{eq:RV:correction} (red crosses) compared to the usual model (green triangles).
The tests of statistical significance on the parameters are presented in Table \ref{table:faculae.test}.
}
    \label{fig:faculae.correction}
\end{center}
\end{figure*}

@@

The right plot of Fig.~\ref{fig:alphacent:corr.gamma} displays the comparison between the RVs derived estimated using the SN density and the Normal density. 
The amplitude of the activity signal is slightly stronger for the SN mean RV (in the top-right plot the black circles of the SN mean RV tend to be more extreme), while the signal measured using N mean RV or SN median RV tend to be similar. 
This behavior is similar to the faculae (see Sec.~\ref{sec:soap.faculae}) suggesting that the activity signal could be due to faculae present on Alpha Centauri B; \jessi{the previous statement seems like rather weak evidence - is there more that could be said to strengthen this point?}
\citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
%When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting. This happens because the mean of the SN is more sensitive to stellar activity. In fact, because the SN includes an asymmetry parameter, SN mean RV gets more shifted in the direction of the asymmetry induced by stellar activity. On the other hand, when using SN median RV, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean. The bottom plot of Fig.~\ref{fig:alphacent:diff:RV} captures this aspect. Both indicators can be used to capture and summarise the different information available in the CCF, as will be shown in the remainder of this work.
%%
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[height = 3in]{HD12862_[2]RadialVelocityDifferences.pdf} 
%   \caption{(top) RVs as function of Julian Day for Alpha Centauri B. The RVs are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses). (bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan crosses).}
%   \label{fig:alphacent:diff:RV}
%\end{figure*}
%
